Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-03 manuscripts/manuscript.Rmd
fix inline code chunk

```{r cross-correlations}
#stats_xcor <- dt[, xcor(fishstock, harvest), by=c("penalty_fn", "reps")]
```

@@

$$
\begin{equation}
\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
\end{equation}
$$

@@

$$\begin{equation}
\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
\end{equation}
$$

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$. (Examples 
shown here use $p$= `r p` and $c_0$ = `r_c0`.) 
<!-- Mention R code provided to test other values? Do we need to test other values?
(i.e. the c0 = 0 case?) Word about units?-->

>>>>

@@

\begin{equation}
\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
\end{equation}

@@

\begin{equation}
\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
\end{equation}

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$. (Examples 
shown here use $p$= `r price` and $c_0$ = `r c0`.) 
<!-- Mention R code provided to test other values? Do we need to test other values?
(i.e. the c0 = 0 case?) Word about units?-->
